Image Caption Generation With CLIP+GPT-2 Model

### 2025-05-04 Latex_Paper/Paper.tex
update all

\begin{abstract}
        This paper presents an image captioning system that combines CLIP with GPT-2.
        We implement a multi-head attention mechanism to effectively bridge the gap between visual and textual modalities. 
        Trained on the MS COCO dataset, 
        our model achieves 94.4\% of human-level consensus quality as 
        measured by CIDEr scores. Our experiments show that the proposed architecture effectively 
        captures both semantic  and syntactic structure in generating natural language descriptions. Additionally, 
        we develop a web-based deployment for real-time captioning that processes images within 10 seconds.
        The results highlight the potential of leveraging pre-trained vision and language 
        models for efficient multimodal understanding with minimal architectural modifications. Codes are avalibale at \url{https://github.com/ChingSsuyuan/Clip_Pro_Caption.git}
\end{abstract}

@@

Our goal is to:
\begin{itemize}
    \item Leverage the pretrained CLIP model to extract semantically rich image embeddings without the need for training a custom vision encoder.
    \item Utilize the generative capabilities of GPT-2 to produce fluent and coherent natural language captions.
    \item Bridge the gap between visual and textual modalities by introducing a projection layer that maps image embeddings into GPT-2's input space.
    \item Enable flexible and data-efficient image captioning, where the visual semantics guide the generation through prefix-based conditioning.
    \item Evaluate the quality of the generated captions using standard metrics such as BLEU and CIDEr, in order to quantitatively assess the model's accuracy and relevance.
\end{itemize}
\pagebreak
\section{Background and Related Work}

>>>>

\begin{abstract}
        This paper presents an image captioning system that combines CLIP with GPT-2.
        We implement a multi-head attention mechanism to effectively bridge between visual and textual modalities. 
        Trained on the MS COCO dataset, 
        our model achieves 94.4\% of human-level consensus quality as 
        measured by CIDEr scores. Our experiments show that the proposed architecture effectively 
        captures both semantic  and syntactic structure in generating natural language descriptions. Additionally, 
        we develop a web-based deployment for real-time captioning
        The results highlight the potential of leveraging pre-trained vision and language 
        models for efficient multimodal understanding with minimal architectural modifications. Codes are avalibale at \url{https://github.com/ChingSsuyuan/Clip_Pro_Caption.git}
\end{abstract}

@@

Our goal is to:
\begin{itemize}
    \item Leverage the pretrained CLIP model to extract semantically rich image embeddings without the need for training a custom vision encoder.
    \item Utilize the generative capabilities of GPT-2 to produce fluent and coherent natural language captions.
    \item Bridge the gap between visual and textual modalities by introducing a projection layer that maps image embeddings into GPT-2's input space.
    \item Enable flexible and data-efficient image captioning, where the visual semantics guide the generation through prefix-based conditioning.
    \item Evaluate the quality of the generated captions using standard metrics such as BLEU and CIDEr, in order to quantitatively assess the model's accuracy and relevance.
\end{itemize}

\section{Background and Related Work}
